---
title: "pacmap"
output: html_document
date: '2022-07-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
```

## PacMAP

Dimensionality reduction that takes the global topology better into account than UMAP.

### Original code and publication

- https://github.com/YingfanWang/PaCMAP  
- https://jmlr.org/papers/v22/20-1061.html  

### Parameters

From the original documentation:

X: numpy.ndarray
    The high-dimensional dataset that is being projected. 
    An embedding will get created based on parameters of the PaCMAP instance.
init: str, optional
    One of ['pca', 'random']. Initialization of the embedding, default='pca'.
    If 'pca', then the low dimensional embedding is initialized to the PCA mapped dataset.
    If 'random', then the low dimensional embedding is initialized with a Gaussian distribution.
save_pairs: bool, optional
    Whether to save the pairs that are sampled from the dataset. Useful for reproducing results.


n_components: int, default=2
    Dimensions of the embedded space. We recommend to use 2 or 3.
n_neighbors: int, default=10
    Number of neighbors considered for nearest neighbor pairs for local structure preservation.
MN_ratio: float, default=0.5
    Ratio of mid near pairs to nearest neighbor pairs (e.g. n_neighbors=10, MN_ratio=0.5 --> 5 Mid near pairs)
    Mid near pairs are used for global structure preservation.
FP_ratio: float, default=2.0
    Ratio of further pairs to nearest neighbor pairs (e.g. n_neighbors=10, FP_ratio=2 --> 20 Further pairs)
    Further pairs are used for both local and global structure preservation.
pair_neighbors: numpy.ndarray, optional
    Nearest neighbor pairs constructed from a previous run or from outside functions.
pair_MN: numpy.ndarray, optional
    Mid near pairs constructed from a previous run or from outside functions.
pair_FP: numpy.ndarray, optional
    Further pairs constructed from a previous run or from outside functions.
distance: string, default="euclidean"
    Distance metric used for high-dimensional space. Allowed metrics include euclidean, manhattan, angular, hamming.
lr: float, default=1.0
    Learning rate of the Adam optimizer for embedding.
num_iters: int, default=450
    Number of iterations for the optimization of embedding. 
    Due to the stage-based nature, we suggest this parameter to be greater than 250 for all three stages to be utilized.
verbose: bool, default=False
    Whether to print additional information during initialization and fitting.
apply_pca: bool, default=True
    Whether to apply PCA on the data before pair construction.
intermediate: bool, default=False
    Whether to return intermediate state of the embedding during optimization.
    If True, returns a series of embedding during different stages of optimization.
intermediate_snapshots: list[int], optional
    The index of step where an intermediate snapshot of the embedding is taken.
    If intermediate sets to True, the default value will be [0, 10, 30, 60, 100, 120, 140, 170, 200, 250, 300, 350, 450]
random_state: int, optional
    Random state for the pacmap instance.
    Setting random state is useful for repeatability.
save_tree: bool, default=False
    Whether to save the annoy index tree after finding the nearest neighbor pairs.
    Default to False for memory saving. Setting this option to True can make `transform()` method faster.
    
### Notes

- The input data must be passed as matrix  

- All parameters passed as integers (e.g., for num_iters) must be passed with an L (e.g., 450L)

### Example

```{r}
use_condaenv("p4r")

source_python("f_pacmap.py")

dimred <- pacmap_fit(as.matrix(iris[,-5]))

plot(dimred, col = iris$Species)
```





