---
title: "parc"
output: html_document
date: '2022-07-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
```

## PARC

"PARC, “phenotyping by accelerated refined community-partitioning” - is a fast, automated, combinatorial graph-based clustering approach that integrates hierarchical graph construction (HNSW) and data-driven graph-pruning with the new Leiden community-detection algorithm."

### Original code and publication

- https://github.com/ShobiStassen/PARC  
- https://academic.oup.com/bioinformatics/article/36/9/2778/5714737  

### Parameters

From the original documentation:

data
(numpy.ndarray) num samples x num features

true_label
(numpy.ndarray) (optional)

dist_std_local
(optional, default = 2) local pruning threshold: the higher the parameter, the more edges are retained

jac_std_global
(optional, default = ‘median’) global level graph pruning. This threshold can also be set as the number of standard deviations below the network’s mean-jaccard-weighted edges. 0.1-1 provide reasonable pruning. higher value means less pruning. e.g. a value of 0.15 means all edges that are above mean(edgeweight)-0.15*std(edge-weights) are retained. We find both 0.15 and ‘median’ to yield good results resulting in pruning away ~ 50-60% edges

random_seed
(optional, default = 42) The random seed to pass to Leiden

resolution_parameter
(optional, default = 1) Uses ModuliartyVP and RBConfigurationVertexPartition

jac_weighted_edges
(optional, default = True) Uses Jaccard weighted pruned graph as input to community detection. For very large datasets set this to False to observe a speed-up with little impact on accuracy

### Notes

- The input data must be passed as matrix  

- All parameters passed as integers (e.g., for dist_std_local) must be passed with an L (e.g., 2L)

### Example

```{r}
use_condaenv("p4r")

source_python("f_parc.py")

source_python("f_pacmap.py")

dimred <- pacmap_fit(as.matrix(iris[,-5]), random_state = 12L)

clust <- unlist(parc_clust(as.matrix(iris[,-5])))

plot(dimred, col = clust+1)
```



